\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{lmodern} % Latin Modern font for pdfLaTeX
\usepackage{fontspec} % Improved font encoding
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[
    colorlinks=true, 
    linkcolor=highlight,
    citecolor=highlight,
    urlcolor=highlight
]{hyperref}
\usepackage{fontawesome5}

% Font and color settings
\renewcommand{\familydefault}{\sfdefault} % Set main font to sans-serif
\definecolor{highlight}{HTML}{4b3069} % Purple highlight color

\pagestyle{empty}

% Define section format
\titleformat{\section}{\Large\bfseries\color{highlight}}{}{}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Customize itemize spacing
\setlist[itemize]{noitemsep, topsep=0pt}

% Header
\def\name{Xander Byrne}
\def\position{Astrophysics PhD Student}
\def\email{
    \href{mailto:xbyrne@ast.cam.ac.uk}{xbyrne@ast.cam.ac.uk}
}
\def\website{
    \href{https://xbyrne.github.io}{xbyrne.github.io}
}
\def\address{
    Institute of Astronomy,
    Cambridge, UK
}
\def\orcid{
    \href{https://orcid.org/0000-0001-9488-238X}{0000-0001-9488-238X}
}

\begin{document}

% Top header
\noindent
\begin{minipage}[t]{0.73\textwidth}
    \vspace{1.2ex} % Adjust spacing as necessary
    {\fontsize{50}{55}\selectfont \textbf{\name}}\\[0.3em]
    {\fontsize{20.5}{30}\textit{\position}}
\end{minipage}
{\color{highlight}\vrule width 1.5pt}
\begin{minipage}[t]{0.27\textwidth}
\raggedleft
{\fontsize{11}{12}\selectfont
\vspace{.3em}
    \address \faMapMarker* \\[.3em]
    \email \faEnvelope[regular] \\[.1em]
    \website \faGithub \\[.3em]
    \orcid \faOrcid
}
\end{minipage}


% Section: Research Interests
\section*{Research Interests}
$\bullet$ Exoplanet composition and habitability
\hspace{1.5em}
$\bullet$ Polluted white dwarfs
\hspace{1.5em}
$\bullet$ Data science \& machine learning

% Section: Education
\section*{Education}
\textbf{Ph.D. in Astronomy}, Institute of Astronomy, University of Cambridge \hfill 2023---\\
Dissertation: \textit{Big-data insights into the white dwarf population}.\\
Supervisor: Dr Amy Bonsor\\

\noindent \textbf{M.Sci in Natural Sciences (Astrophysics)}, University of Cambridge \hfill 2019--23 \\
Graduated 1st class with distinction.

% Section: Publications
\section*{Publications}

\begin{itemize}
    \item \textbf{X.~Byrne}, A.~Bonsor, L.~K.~Rogers et al. (2024). 
    \textit{Semi-supervised spectral classification of DESI white dwarfs by dimensionality reduction}. 
    MNRAS, in press.
    \href{https://doi.org/10.1093/mnras/stae2478}{doi:10.1093/mnras/stae2478}
    \item \textbf{X.~Byrne}, R.~A.~Meyer, E.~P.~Farina, et al. (2024).
    \textit{Quasar Island - three new $z\sim6$ quasars, including a lensed candidate, identified with contrastive learning}.
    MNRAS, 530(1), 870-880.
    \href{https://doi.org/10.1093/mnras/stae902}{doi:10.1093/mnras/stae902}.
    \item \textbf{X.~Byrne}, O.~Shorttle, S.~Jordan et al. (2024).
    \textit{Atmospheres as a Window to Rocky Exoplanet Surfaces}.
    MNRAS, 527(4), 10748-10759.
    \href{https://doi.org/10.1093/mnras/stad3914}{doi:10.1093/mnras/stad3914}.
\end{itemize}

% Section: Awards and Honors
\section*{Awards, Grants etc.}
\begin{itemize}
    \item \textbf{MASt/Part III Bursary} (£3500) \hfill Institute of Astronomy\\
    Funding the conversion of my Masters' thesis to a published paper over the course of a summer internship.
    \item \textbf{MPIA Summer Internship} (€3750) \hfill Max-Planck-Institut f\"{u}r Astronomie\\
    Funding a summer internship: \textit{Searching for Lensed High-Redshift Quasars using Unsupervised Machine Learning}.
    \item \textbf{Winifred Georgia Holgate-Pollard Memorial Prize} (£1650)
    \hfill University of Cambridge\\
    Awarded for the best performance in the Natural Sciences (Astrophysics) examinations.
    \item \textbf{John Spencer Wilson Prize} (£500) \hfill St Catharine's College, Cambridge\\
    Awarded in recognition of exceptional performance in the Natural Sciences examinations.
\end{itemize}

% Section: Telescope Time

\section*{Awarded Telescope Time}
% \subsection*{As PI}

\subsection*{As Co-I}

\begin{itemize}
    \item \textit{White dwarfs as a means to probe core formation in exoplanetary systems}; PI Rogers\\
    65h VLT/X-Shooter spectroscopy (115.28F4)
    \item \textit{Characterising a $z\sim6$ gravitationally-lensed BAL quasar candidate}; PI Meyer\\
    2.9h VLT/X-Shooter spectroscopy (113.26CY)
    \item \textit{Measuring the mass of the SMBHs powering two lensed $z\sim6$ quasars}; PI Meyer\\
    4.23h Gemini (DDT) FLAMINGOS-2 spectroscopy (DT-2022B-029)
\end{itemize}


% Section: Skills
\section*{Technical Experience}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, C++, MATLAB
    \item \textbf{Astronomy Software:} EsoRex, EsoReflex, DS9, TOPCAT, PyTorch, TensorFlow
\end{itemize}

% Section: Teaching Experience
\section*{Teaching}
\noindent \textbf{Supervisor}, Part II Astrophysics, University of Cambridge \hfill 2023---
\begin{itemize}
    \item Conducted small-group teaching, marking solutions 
    \begin{itemize}
        \item \textit{Relativity} (GR): 8 students
        \item \textit{Stellar Dynamics \& Structure of Galaxies} (orbits \& potentials): 8 students
    \end{itemize}
    \item Produced popular revision notes ($\sim2500$ hits per year)
\end{itemize}

% Section: Talks
\section*{Talks}

\subsection{Invited Talks}

\begin{itemize}
\vspace{1ex}
\item \textbf{ExoCoffee -- MPIA, Heidelberg} \hfill Feb 2024\\
\textit{Atmospheres as a Window to Rocky Planet Surfaces}

\item \textbf{Data Intensive Science Seminar Series -- Maxwell Centre, Cambridge} \hfill Feb 2024\\
\textit{Contrastive Learning and High-Redshift Quasars}

\item \textbf{Physics Evening -- St Catharine's College, Cambridge} \hfill May 2023\\
\textit{Worlds Anew: Exoplanets and their Characterisation}
\end{itemize}

\subsection{Contributed Talks}

\begin{itemize}
\vspace{1ex}

\item \textbf{Wednesday Seminar Series -- Institute of Astronomy, Cambridge} \hfill Oct 2024\\
\textit{Spectral Classification of White Dwarfs by Dimensionality Reduction}

\item \textbf{Astro Data Science Discussion Group -- KICC, Cambridge} \hfill Jan 2024\\
\textit{Contrastive Learning and High-Redshift Quasars}

\item \textbf{Galaxy Coffee -- MPIA, Heidelberg} \hfill Sep 2022\\
\textit{Searching for Gravitationally-Lensed High-Redshift Quasars with Unsupervised Machine Learning}

\end{itemize}

\section*{Professional Service}

\begin{itemize}
\item \textbf{Organiser, Wednesday Seminar Series}
\hfill 2024---\\
A long-running seminar series given by PhD students and postdocs at the Institute of Astronomy.
\item \textbf{Organiser, PhD/Postdoc Jamboree}
\hfill Oct 2024\\
A social `introduction' event for the Institute's PhDs and postdocs.
\item \textbf{Tech Assistant, \textit{IoA50} conference}
\hfill Jul 2024\\
Assisting speakers at a large conference with presentations, mics etc.
\item \textbf{Organiser, Undergraduate Journal Club} \hfill 2023--24\\
A journal club for undergraduates, also offering career advice.
\end{itemize}

\section*{Outreach}

\begin{itemize}
    \item \textbf{\textit{The Naked Scientists}, BBC Radio 5 Live}
    \hfill Mar 2023---\\
    National radio show and podcast. Several appearances both live and in pre-recorded segments
    \item \textbf{Public Open Evenings, Institute of Astronomy}
    \hfill 2022---\\
    Visits for the general public, involving a public lecture and stargazing.
    \item \textbf{Cambridge Hands-On Science (CHaOS) event: \textit{Crash Bang Squelch}}
    \hfill Mar 2024\\
    Outreach talk: \textit{How to find an Alien Planet}
    \item \textbf{Birmingham Schools Science Network}
    \hfill Sep 2023\\
    Outreach talk: \textit{Worlds Anew: Quasars, Exoplanets, and the Search for Life}.
    \item \textbf{HiSPARC Project}
    \hfill 2018--22\\
    Teaching sessions and sparking research projects for high-school physics students, particularly girls
    \item \textbf{\textit{Varsity Sci 2021}}
    \hfill Oct 2021\\
    Outreach talk: \textit{The Messier Catalogue: 110 objects in 10 minutes}.
    \item \textbf{Cambridge University Physics Society}
    \hfill Aug 2020\\
    Outreach talk: \textit{Negative mass: matter that's lighter than light}.
\end{itemize}

\section*{Press Coverage}

\begin{itemize}
    \item \textbf{NOIRLab Stories Blog}: \href{https://noirlab.edu/public/blog/cosmic-gems/}{\textit{AI Aids in Search for Cosmic Gems in Ocean of Data}}
    \hfill Jul 2024
\end{itemize}



\end{document}
